---
title: "SS4853"
author: "Fang He"
date: "December 8, 2015"
output: pdf_document
---


### Notes from my time (2012)


Use the data file from the 2011 Youth Risk Behavior Survey. Calculate two new variables from the dataset: 

* body mass index (BMI), which is a preson's weight in kilograms divided by their height in meters squared.

* age of the student (it is a coded value in the data file).

<br>

1. Using linear regression find the variables in the data file that best explain the variation in BMI. Make appropriate plots of the data.

In answering this question, you should research information about BMI and its correlates. To get you started, here is one article that will be of interest.

T.Ostbye, J.Pomerlau, M.Speechley, L.L. Pederson and K.L. Speechle (1995). Correlates of body mass index in the 1990 Ontario Health Survey. *Canadian Medical Association Journal* **152** (11): 1811 -- 1817



2. Using logistic regression find the variables in the data file that best explain the proportion of students who have contemplated suicide. Make appropriate plots of the data.

In answering this question, you should research information about teen suicide and its correlates. To get you started, here is one article that will be of interest.

M.H. Swahn and R.M. Bossarte (2007). Gender, early alcohol use, and suicide ideation and attempts: findings from the 2005 Youth Risk Behavior Survey. *Journal of Adolescent Health* **41** (2): 175 -- 181



### First Class

What effects BMI? (Do test)

Test whether sex is significant. 

Add random effect in the same model to see how p-value of sex change.


### Second Class

Do logistic regression on suicide data.


## Details

```{r}
yrbs <- read.table("/Users/fhe7/Documents/School/Sampling/yrbs2013.txt",header=TRUE)
head(yrbs)

colnames(yrbs[,c(2,3,7,8)]) <- c("age","sex","height","weight")
attach(yrbs)

bmi <- q7/q6^2
```

```{r}
hist(bmi,prob=TRUE)
lines(density(bmi,na.rm = T),col=2,lwd=1.5)
```

### Linear Regression

Q: Why we use linear regression?

```{r}
plot(bmi~factor(q1))
plot(bmi~factor(q2))
```


```{r}
mod0 <- lm(bmi ~ factor(q1)+factor(q2),data=yrbs)
summary(mod0)
```

age - young did not affect much of BMI

gender - different


```{r}
mod1 <- update(mod0,.~.-factor(q1))
## or mod1 <- lm(bmi ~ factor(q2),data=yrbs)
summary(mod1)
```

```{r}
anova(mod1,mod0)
```

### Consider random effect

```{r results='hide',message=FALSE}
library(lme4)
```

```{r}
mod0_lmer <- lmer(bmi ~ q2 + factor(stratum) + (1|psu),data=yrbs)
summary(mod0_lmer)
```


Final Project - survey design - modeling with random effect - see the difference 














